Modal type theory based on the intuitionistic epistemic logic

### 2018-01-20 article.tex
added
added more draft

@@

  \bibitem{Abe} T. Abe. Completeness of modal proofs in first-order predicate logic. Computer Software, JSSST Journal, 24:165 -- 177, 2007.
  \end{thebibliography}

>>>>

We will consider term model for simply typed lambda calculus $\times$ and $\to$ standardly described in \cite{LambekScott} \cite{Abramsky}.

\begin{defin}
  Let us define an endofunctor $\mathcal{K} : \mathcal{C}(\lambda) \to \mathcal{C}(\lambda)$, such that:
  \begin{itemize}
    \item ${\bf K} : A \mapsto {\bf K}A$;
    \item ${\bf K} : [x,M] \in Hom_{\mathcal{C}(\lambda)}(A,B) \mapsto \text{fmap } f = [y, {\bf let \: pure \:} x = y \in M] \in Hom_{\mathcal{C}(\lambda)}({\bf K} A, {\bf K} B)$.
  \end{itemize}
\end{defin}

\begin{lemma} Functoriality

  i) ${\bf K}(g \circ f) = {\bf K}(g) \circ {\bf K}(f)$;

  ii) ${\bf K}(id_A) = id_{{\bf K}A}$.
\end{lemma}

Easy checking.

\begin{defin}

  Let us define natural transformations:
  \begin{itemize}
  \item $\eta : Id_{\mathcal{C}(\lambda)} \to \mathcal{K}$, such that forall $A \in Ob_{\mathcal{C}(\lambda)}$, $\eta_A = [x, {\bf pure \:} x] \in Hom_{\mathcal{C}(\lambda)}(A, {\bf K}A)$;

  \item $\ast_{A,B} : {\bf K}A \times {\bf K}B \to {\bf K}(A \times B)$
  \end{itemize}
\end{defin}

\begin{lemma} Naturality for $\eta$ and for $\ast$

  i) $\text{fmap } f \circ \eta_A = \eta_B \circ f$;

  ii) $\text{fmap } (f \times g) \circ \ast_{A, B} = \ast_{C,D} \circ (\text{fmap } f) \times (\text{fmap } g)$.

  iii) $\ast_{A,B} \circ (\eta_{A} \times \eta_{B}) = \eta_{A \times B}$;
\end{lemma}

  i) $\text{fmap } f \circ \eta_A = \eta_B \circ f$

$\begin{array}{lll}
&\eta_B \circ f = & \\
&[y, {\bf pure \:} y] \circ [x, M] = & \\
&[x, {\bf pure \:} y [y := M]] =& \\
&[x, {\bf pure \:} M]& \\
&\text{On the other hand}& \\
&\text{fmap } f \circ \eta_A = &\\
&[z, {\bf let \: pure \:} x = z {\: \bf in \:} M] \circ [x, {\bf pure \: x}] = & \\
&[x, {\bf let \: pure \:} x = z {\: \bf in \:} M [z := {\bf pure \:} x]]& \\
&[x, {\bf let \: pure \:} x = {\bf pure \: x} {\: \bf in \:} M]& \\
&[x, {\bf pure \:} M [x := x]]& \\
&[x, {\bf pure \:} M]&
\end{array}$

ii)  $\text{fmap } (f \times g) \circ \ast_{A, B} = \ast_{C,D} \circ (\text{fmap } f) \times (\text{fmap } g)$

\begin{lemma} Tensorial strength
\end{lemma}

\begin{lemma}

  ${\bf K}$ is an applicative functor.
\end{lemma}

\begin{theorem} Completeness

  Let $[\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$, then $M =_{\beta \eta} N$.
\end{theorem}

@@

  \bibitem{Abe} T. Abe. Completeness of modal proofs in first-order predicate logic. Computer Software, JSSST Journal, 24:165 -- 177, 2007.

  \bibitem{LambekScott}

  \bibitem{Abramsky}

  \bibitem{Gabbay}

\end{thebibliography}
